Self-reported LLM usage and outcomes on a data science project: Evidence from two undergraduate data science courses

### 2025-04-12 paper/paper.qmd
Reformatted table 6 to put (MAD) on same line as estimate to improve readability, and modified the caption

```{r tbl-model-results-full}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Coefficient estimates and mean absolute deviation (MAD)

modelsummary(
  list(
    "STA302" = fit1,
    "STA302: GPA" = fit2,
    "STA304" = fit3,
    "STA304: GPA" = fit4,
    "STA304: GPA & ESL" = fit5
  ),
  statistic = "mad",
  fmt = 2,
  output = "kableExtra",
  kable_options = list(booktabs = TRUE, linesep = ""),
  # coef_map = c(
  #   "b_Intercept" = "Intercept",
  #   "b_phi_Intercept" = "Intercept (Phi)",
  #   "b_zoi_Intercept" = "Intercept (ZOI)",
  #   "b_llm_usageSomewhat" = "LLM usage: Somewhat",
  #   "b_llm_usageExtensive" = "LLM usage: Extensive",
  #   "b_phi_llm_usageSomewhat" = "LLM usage: Somewhat (Phi)",
  #   "b_phi_llm_usageExtensive" = "LLM usage: Extensive (Phi)",
  #   "b_what_is_your_gpa" = "GPA",
  #   "b_phi_what_is_your_gpa" = "GPA (Phi)",
  #   "b_native_englishYes" = "English native: Yes",
  #   "b_phi_native_englishYes" = "English native: Yes (Phi)"
  # )
) |>
  kableExtra::kable_styling(font_size = 7)
```

>>>>

```{r tbl-model-results-full}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Coefficient estimates and mean absolute deviation (MAD) for five fitted models

modelsummary(
  list(
    "STA302" = fit1,
    "STA302: GPA" = fit2,
    "STA304" = fit3,
    "STA304: GPA" = fit4,
    "STA304: GPA & ESL" = fit5
  ),
  statistic = NULL,
  estimate = "{estimate} ({mad})",
  fmt = 2,
  output = "kableExtra",
  kable_options = list(booktabs = TRUE, linesep = ""),
  # coef_map = c(
  #   "b_Intercept" = "Intercept",
  #   "b_phi_Intercept" = "Intercept (Phi)",
  #   "b_zoi_Intercept" = "Intercept (ZOI)",
  #   "b_llm_usageSomewhat" = "LLM usage: Somewhat",
  #   "b_llm_usageExtensive" = "LLM usage: Extensive",
  #   "b_phi_llm_usageSomewhat" = "LLM usage: Somewhat (Phi)",
  #   "b_phi_llm_usageExtensive" = "LLM usage: Extensive (Phi)",
  #   "b_what_is_your_gpa" = "GPA",
  #   "b_phi_what_is_your_gpa" = "GPA (Phi)",
  #   "b_native_englishYes" = "English native: Yes",
  #   "b_phi_native_englishYes" = "English native: Yes (Phi)"
  # )
) |>
  kableExtra::kable_styling(font_size = 7)
```
